Parallel Algorithms for the Probabilistic Roadmap Method for Robotic Motion Planning with GPU Acceleration

### 2016-07-31 paper/paper.tex
kleine quellenergaenzung: roboterdynamik buch

The probabilistic roadmap algorithm is applied  to create collision-free trajectories of a robot arm.
For a robot with given joint angles \(q_i\) one can calculate straightforward all positions and orientations  of the single parts of the robot.
For this, coordinate frames according to the Denavit-Hartenberg (DH) \cite{robodyn} convention are used.
The coordinate frames of reference of the single parts are described by transformation matrices 
$T_i \in \R^{4 \times 4}, i=1,...,d$, which transform points from the body frame of reference into the world frame of reference. They depend on the state $q=(q_1,...,q_d)^T$ of the robot and on the geometry of the joint angles given by the DH parameters of the robot.

@@

One can show, that by an proper choice of the body frames, every robot with rotational or prismatic joints can be described by such a set of DH parameters, i.e. there exists a set of parameters, such that the above definition leads to the correct transformations for this robot.
For the exact calculations, see \cite{robodyn}.

@@

\begin{thebibliography}{}%{999}
	\bibitem{prmlec} D. Burschka, Lecture Robot Motion Planning, \url{http://robvis01.informatik.tu-muenchen.de/courses/wegtraj/index.html}
	\bibitem{prm1} H. Choset, K. Lynch, S. Hutchinson, G. Kantor, W. Burgard, L. Kavraki and S. Thrun, Principles of Robot Motion: Theory, Algorithms, and Implementation, MIT Press 2005
	\bibitem{prm2} S. M. LaValle, Planning Algorithms, Cambridge University Press 2006
	\bibitem{robodyn} T. Buschmann, Skript zur Vorlesung: Roboterdynamik SS14, Lehrstuhl für Angewandte Mechanik, TU München 2014
	\bibitem{chung} K. Chung, Wenping Wang, Quick Collision Detection of Polytopes in Virtual Environments, Proceedings of the ACM Symposium on Virtual Reality Software and Technology (VRST 96), Mark Green (ed.) 1996
	\bibitem{ericson} C. Ericson, Real-Time Collision Detection, MK 2005
	\bibitem{cuda} Nvidia Corporation, Cuda Programming Guide, 2015, \url{http://docs.nvidia.com/cuda/pdf/CUDA_C_Programming_Guide.pdf}
	\bibitem{cuda2} D. B. Kirk, W. W. Hwu, Programming Massively Parallel Processors, MK 2010
	\bibitem{c++} Pitt-Francis, Guide to Scientific Computing in C++, Springer 2012
	\bibitem{mpi} W. Gropp, Using MPI: Portable Parallel Programming with the Message-Passing Interface, MIT Press 2014
	\bibitem{githubcode} M. Demmeler, Github Repository GPUPRM, \url{https://github.com/demmeler/GPUPRM}
\end{thebibliography}

>>>>

The probabilistic roadmap algorithm is applied  to create collision-free trajectories of a robot arm.
For a robot with given joint angles \(q_i\) one can calculate straightforward all positions and orientations  of the single parts of the robot.
For this, coordinate frames according to the Denavit-Hartenberg (DH) \cite{robodyn}, \cite{robodynbuch} convention are used.
The coordinate frames of reference of the single parts are described by transformation matrices 
$T_i \in \R^{4 \times 4}, i=1,...,d$, which transform points from the body frame of reference into the world frame of reference. They depend on the state $q=(q_1,...,q_d)^T$ of the robot and on the geometry of the joint angles given by the DH parameters of the robot.

@@

One can show, that by an proper choice of the body frames, every robot with rotational or prismatic joints can be described by such a set of DH parameters, i.e. there exists a set of parameters, such that the above definition leads to the correct transformations for this robot.
For the exact calculations, see \cite{robodyn}, \cite{robodynbuch}.

@@

\begin{thebibliography}{}%{999}
	\bibitem{prmlec} D. Burschka, Lecture Robot Motion Planning, \url{http://robvis01.informatik.tu-muenchen.de/courses/wegtraj/index.html}
	\bibitem{prm1} H. Choset, K. Lynch, S. Hutchinson, G. Kantor, W. Burgard, L. Kavraki and S. Thrun, Principles of Robot Motion: Theory, Algorithms, and Implementation, MIT Press 2005
	\bibitem{prm2} S. M. LaValle, Planning Algorithms, Cambridge University Press 2006
	\bibitem{robodyn} T. Buschmann, Skript zur Vorlesung: Roboterdynamik SS14, Lehrstuhl für Angewandte Mechanik, TU München 2014
	\bibitem{robodynbuch} F. Pfeiffer, E. Reithmeier, Roboterdynamik, B.G. Teubner Verlag 1987
	\bibitem{chung} K. Chung, Wenping Wang, Quick Collision Detection of Polytopes in Virtual Environments, Proceedings of the ACM Symposium on Virtual Reality Software and Technology (VRST 96), Mark Green (ed.) 1996
	\bibitem{ericson} C. Ericson, Real-Time Collision Detection, MK 2005
	\bibitem{cuda} Nvidia Corporation, Cuda Programming Guide, 2015, \url{http://docs.nvidia.com/cuda/pdf/CUDA_C_Programming_Guide.pdf}
	\bibitem{cuda2} D. B. Kirk, W. W. Hwu, Programming Massively Parallel Processors, MK 2010
	\bibitem{c++} Pitt-Francis, Guide to Scientific Computing in C++, Springer 2012
	\bibitem{mpi} W. Gropp, Using MPI: Portable Parallel Programming with the Message-Passing Interface, MIT Press 2014
	\bibitem{githubcode} M. Demmeler, Github Repository GPUPRM, \url{https://github.com/demmeler/GPUPRM}
\end{thebibliography}
